---
title: "Demographics"
author: "Meg Hutch"
date: "3/22/2021"
output: html_document
---

**Do we have the number of patients who have been discharged? Is it correct to have all the patients listed for the time to discharge in the table 1? -- I could calculate based on survival curve numbers?**

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(gridGraphics)
library(gridExtra)
library(ggpubr)
library(DT)
library(kableExtra)
library(cowplot)
library(RColorBrewer)
library(glue)
theme_set(theme_bw() +
  theme(panel.grid.minor = element_blank()))
```

```{r}
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}

rm(rdas, rda)
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"

site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)
sorted_sites <- site_avails %>%
  filter(date_v3_received == 1) %>%
  pull(siteid) %>%
  paste("results", sep = "_")

sites_wo_race <- site_params %>%
  filter(!include_race) %>%
  pull(siteid)

# colorBlindGrey6 <-
#   c("#0072B2", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#CC79A7")
```


```{r}
results <- mget(ls(pattern = "results"))
```


## Demographic Data

### Pre-processing

```{r}
demo_table_list <- list()

for (i in sorted_sites) {
  tmp <- get(i)
  demo_table_list[[i]] <- tmp[[c(
    "first_hosp_results",
    "cpns_results",
    "demo_table"
  )]] %>%
    select(site, everything())
}
combined_table_wide <- bind_rows(demo_table_list) %>%
  # site level differences in variable names require tolower()
  # rename race.other to avoid recoding conflicts with age_group.other
  mutate(
    site = toupper(site),
    variable = tolower(variable),
    variable = if_else(variable == "race.other", "race.Other", variable),
    variable = if_else(variable == "age_group.other", "age_group.Unknown", variable),
    Demo_var = sub("\\..*", "", variable),
    Demo_var_i = sub(".*\\.", "", variable) %>%
      gsub("_", " ", .) %>%
      str_to_title() %>%
      recode(
        `00to02` = "0-2",
        `03to05` = "3-5",
        `06to11` = "6-11",
        `12to17` = "12-17",
        `18to25` = "18-25",
        `26to49` = "26-49",
        `50to69` = "50-69",
        `70to79` = "70-79",
        `80plus` = "80+",
        race.white = "White",
        race.american_indian = "American Indian",
        `Hawaiian Pacific Islander` = "Hawaiian/Pacific Islander",
        `Hispanic Latino` = "Hispanic/Latino",
        `False` = "Not Readmitted",
        `True` = "Readmitted"
      )
  )
```

```{r}
other_table_list <- list()
for (i in sorted_sites) {
  tmp <- get(i)
  other_table_list[[i]] <- tmp[[c(
    "first_hosp_results",
    "cpns_results",
    "other_obfus_table"
  )]] %>%
    select(site, everything())
}

# create a function to back transform the pre-admission scores which were performed as log(n + 1)
combined_other_table_wide <- bind_rows(other_table_list) %>%
  filter(grepl("Mean|Median", name))

transform_count <- function(x) {
  
  exp(x) - 1
  
}

# here we transform the median admission scores and round them
combined_other_table_wide_pre_adm <- combined_other_table_wide %>% 
  filter(name == "Median pre admission cns [Min, Max]" | name == "Median pre admission pns [Min, Max]") %>% 
  separate(None, c("None_first", "None_min", "None_max"), sep=" ") %>% 
  separate(Central, c("CNS_first", "CNS_min", "CNS_max"), sep=" ") %>% 
  separate(Peripheral, c("PNS_first", "PNS_min", "PNS_max"), sep=" ") %>% 
  mutate(across(None_first:CNS_max, ~ gsub("\\[|\\]", "", .x))) %>% 
  mutate(across(None_first:CNS_max, ~ gsub(",", "", .x))) %>% 
  mutate(across(None_first:CNS_max, ~ as.numeric(.) %>% 
                  transform_count(.) %>% 
                  round(., 1))) %>% 
  mutate(None = paste0(None_first, " [", None_min, ",", None_max, "]"),
         Central = paste0(CNS_first, " [", CNS_min, ",", CNS_max, "]"),
         Peripheral = paste0(PNS_first, " [", PNS_min, ",", PNS_max, "]")) %>% 
  select(site, name, None, Peripheral, Central)

# remove the old pre-admission scores
combined_other_table_wide <- combined_other_table_wide %>% 
  filter(!name == "Median pre admission cns [Min, Max]",
         !name == "Median pre admission pns [Min, Max]",
         !name == "Mean pre admission cns (SD)",
         !name == "Mean pre admission pns (SD)")

# add revised pre-admission scores
combined_other_table_wide <- rbind(combined_other_table_wide, 
                                   combined_other_table_wide_pre_adm)
```


```{r}
vars_to_process <- unique(combined_other_table_wide$name)

processed_list <- list()

for (i in vars_to_process) {
  mod_table <- combined_other_table_wide %>%
    rename("var" = name) %>%
    filter(var == i) %>%
    mutate(
      site = toupper(site),
      None = sub("(\\(.*|\\[.*)", "", None),
      Peripheral = sub("(\\(.*|\\[.*)", "", Peripheral),
      Central = sub("(\\(.*|\\[.*)", "", Central)
    ) %>%
    mutate(across(None:Central, as.numeric)) %>%
    as_tibble() %>%
    select(-site, -var) %>%
    summarise_all(list(
      mean = mean,
      median = median,
      min = min,
      max = max
    ),
    na.rm = TRUE
    )

  processed_list[[i]] <- mod_table
}

# Mean of the median distribution is the best estimate for the median:
# It's the BLUE[est] (best least unbiased estimator).
other_table_compiled <- bind_rows(processed_list, .id = "Table 1") %>%
  # select(-contains("mean")) %>%
  filter(grepl("Median", `Table 1`)) %>%
  mutate(across(ends_with("mean"), ~ round(., 1))) %>%
  # get average of the medians
  mutate(
    None = glue("{None_mean} [{None_min}, {None_max}]"),
    Peripheral = glue("{Peripheral_mean} [{Peripheral_min}, {Peripheral_max}]"),
    Central = glue("{Central_mean} [{Central_min}, {Central_max}]"),
    N = NA
  ) %>%
  select(`Table 1`, N, None, Peripheral, Central)
```

## Table One

```{r}
ordered_vars <- c(
  "all", "sex", "age_group", "race",
  "readmitted", "severity", "survival"
)
tableOne_inter <- combined_table_wide %>%
  group_by(variable, Demo_var, Demo_var_i) %>%
  summarise(across(
    starts_with("n_var"),
    function(x) sum(x, na.rm = TRUE)
  ), .groups = "drop")

row_order <- c(
  "All Patients", "Female", "Male",
  "0-2", "3-5", "6-11", "12-17", "18-25",
  "26-49", "50-69", "70-79", "80+", "Unknown",
  "American Indian", "Asian", "Black",
  "Hawaiian/Pacific Islander",
  "Hispanic/Latino", "White", "Other",
  "Median Elixhauser score [Min, Max]",
  "Median pre admission cns [Min, Max]",
  "Median pre admission pns [Min, Max]",
  "Non-Severe", "Severe",
  "Median time to severe [Min, Max]",
  "Alive", "Deceased", 
  "Median time to death [Min, Max]",
  "Median time to first discharge [Min, Max]",
  "Not Readmitted", "Readmitted",
  "Median time to first readmission [Min, Max]",
  "Median number of readmissions [Min, Max]"
)

get_table_n <- function(var) {
  tableOne_raw %>%
    filter(`Table 1` == var) %>%
    pull(N)
}

tableOne_raw <- tableOne_inter %>%
  filter(Demo_var == "sex") %>%
  summarise(across(where(is.numeric), sum)) %>%
  data.frame(
    variable = "all",
    Demo_var = "all",
    Demo_var_i = "All Patients",
    .
  ) %>%
  bind_rows(tableOne_inter) %>%
  mutate(
    N = rowSums(across(where(is.numeric))),
    Demo_var = factor(Demo_var, levels = ordered_vars)
  ) %>%
  group_by(Demo_var) %>%
  mutate(across(
    starts_with("n_var"),
    function(x) {
      paste0(x, " (", round(x / sum(x, na.rm = TRUE) * 100, 1), "%", ")")
    }
  )) %>%
  ungroup() %>%
  arrange(Demo_var) %>%
  select(Demo_var_i, N, starts_with("n_var")) %>%
  `colnames<-`(gsub(
    x = names(.),
    pattern = "n_var_",
    replacement = ""
  )) %>%
  rename("Table 1" = Demo_var_i) %>%
  bind_rows(other_table_compiled) %>%
  slice(match(row_order, `Table 1`))

tableOne_compiled <- tableOne_raw %>%
  mutate(
    N = case_when(
      grepl("Median time to first discharge", `Table 1`) ~ get_table_n("All Patients"),
      grepl("Median time to last discharge", `Table 1`) ~ get_table_n("All Patients"),
      grepl("Median time to severe", `Table 1`) ~ get_table_n("Severe"),
      grepl("death", `Table 1`) ~ get_table_n("Deceased"),
      grepl("readmission", `Table 1`) ~ get_table_n("Readmitted"),
      grepl("Median Elixhauser score", `Table 1`) ~ get_table_n("All Patients"),
      TRUE ~ N
    )
  ) %>% 
  mutate(N = if_else(`Table 1` == "Median pre admission pns [Min, Max]" | `Table 1` == "Median pre admission cns [Min, Max]", 
              get_table_n("All Patients"), N))

tableOne_compiled <- tableOne_compiled %>% 
  select(`Table 1`, N, None, Central, Peripheral) 

kbl(tableOne_compiled) %>%
  add_header_above(c(
    " ",
    "No Neurological Disease" = 1,
    "Neurological Disease" = 3
  )) %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Sex", 2, 3) %>%
  pack_rows("Age", 4, 13) %>%
  pack_rows("Race & Ethnicity", 14, 20) %>%
  pack_rows("Past Medical History", 21, 23) %>%
  pack_rows("Severity", 24, 26) %>%
  pack_rows("Survival", 27, 29) %>%
  pack_rows("Discharge & Readmission", 30, 34)

write.csv(tableOne_compiled, "manuscript/Table1.csv", row.names = FALSE)
```

```{r fig.height=15, fig.width=11}
combined_table <- combined_table_wide %>%
  pivot_longer(
    cols = starts_with("n_var"),
    names_to = "Dx",
    values_to = "Count"
  ) %>%
  replace_na(list(Count = 0)) %>%
  mutate(Dx = gsub("n_var_", "", Dx) %>%
    fct_relevel(c("None", "Central", "Peripheral")))
```

### Evaluate demographic/clinical characteristics among neurostatus groups

```{r}
# total patients
N = tableOne_compiled %>% select(N) %>% head(1) %>% as.numeric()

# sum of all neuro condition groups
cns_n = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Central"]))
pns_n = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Peripheral"]))
none_n = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"None"]))

vars = tableOne_inter$variable

# for binary variables, we should group. 
# Thus, only run the analysis for sex.male rather than both sex.female AND sex.male which would be duplicative

exclude <- c("readmitted.false", "sex.female", "survival.deceased", "severity.non-severe")

vars <- vars[!vars %in% exclude]

calc_chisq <- function(var) {
  
  # define matrix for each variable
  mat <- tableOne_inter %>% 
  filter(variable == paste(var)) %>% 
  select(starts_with("n_var")) %>% 
  mutate(none_dif = none_n - n_var_None,
         pns_dif = pns_n - n_var_Peripheral, 
         cns_dif = cns_n - n_var_Central) %>% 
  as.integer() %>% 
  matrix(nrow = 2, ncol = 3, byrow = TRUE) 

  result <- chisq.test(unlist(mat))
  
}

chi_result_list = list()

for(i in vars) {
  
  print(i)
  
  test = calc_chisq(i)
  X2 <- round(test$statistic, 4)
  p_value <- test$p.value
  df <- test$parameter
  Variable = paste(i)
  
  results <- cbind(Variable, X2, p_value, df) %>% 
    data.frame() 
  
  rownames(results) <- NULL
  
  chi_result_list[[i]] <- results
}

chisq_results <- bind_rows(chi_result_list)
```

Anova tests for continuous variables

```{r}
processed_list_figs <- list()
for (i in vars_to_process) {
  mod_table <- combined_other_table_wide %>%
    rename("var" = name) %>%
    filter(var == i) %>%
    mutate(
      site = toupper(site),
      None = sub("(\\(.*|\\[.*)", "", None),
      Peripheral = sub("(\\(.*|\\[.*)", "", Peripheral),
      Central = sub("(\\(.*|\\[.*)", "", Central)
    ) %>%
    mutate(across(None:Central, as.numeric))

  processed_list_figs[[i]] <- mod_table
}

other_table_for_figs <- bind_rows(processed_list_figs)

# format the continuous variables
cont_vars = other_table_for_figs %>%
  mutate(
    me = stringr::word(var),
    grouped_var = gsub("Mean |Median | \\[Min, Max\\]| \\(SD\\)", "", var)
  ) %>%
  pivot_longer(
    cols = None:Central,
    names_to = "type"
  ) %>%
  mutate(type = factor(type, levels = c("None", "Central", "Peripheral"))) %>% 
  filter(me == "Median",
         grouped_var %in% c("Elixhauser score",
                            "pre admission cns", 
                            "pre admission pns", 
                            "time to death", 
                            "time to first discharge", 
                            "time to severe",
                            "number of readmissions",
                            "time to first readmission")) %>% 
  distinct()

# anova
cont_var_results <- function(variable) {
  
  df <- cont_vars %>% 
  filter(grouped_var == paste(variable))
  
  # kruskal.test calculates the kruskal-Wallis H-statistic to compare the means (or is it medians?);
  # does not assume normality between groups
  # also called the one-way ANOVA on ranks
  test = kruskal.test(df$value ~ df$type)
  
}

cont_vars_list = list()

outcome_cont_vars = unique(cont_vars$grouped_var)

for(i in outcome_cont_vars) {
  
  test = cont_var_results(i)
  X2 <- round(test$statistic, 4)
  p_value <- test$p.value
  df <- test$parameter
  Variable = paste(i)
  
  results <- cbind(Variable, X2, p_value, df) %>% 
    data.frame() 
  
  rownames(results) <- NULL
  
  cont_vars_list[[i]] <- results

  
}

anova_results <- bind_rows(cont_vars_list)
```

Combine chisquare and anova results

```{r}
demo_stats <- rbind(chisq_results %>% select(Variable, p_value),
                    anova_results %>% select(Variable, p_value))

# adjust p-values with FDR
demo_stats$adj_p_value <- p.adjust(demo_stats$p_value, method = "fdr")

demo_stats <- demo_stats %>% 
  mutate(p_value = as.numeric(p_value),
         pvalue = if_else(p_value < 0.001, "< 0.001", paste(round(p_value, 3))),
         adj.p_value = if_else(adj_p_value < 0.001, "< 0.001", paste(round(adj_p_value, 3))))

write.csv(demo_stats, "manuscript/Table1_pvals.csv", row.names = FALSE)
```

Evaluate anova results

```{r}
# https://rcompanion.org/rcompanion/d_06.html
# Dunn test for multiple comparisons
library(rcompanion)
library(FSA)
discharge = cont_vars %>% filter(grouped_var == "time to first discharge")
pos_hoc = dunnTest(discharge$value ~ discharge$type,
              data=discharge,
              method="bh")

pos_hoc <- pos_hoc$res
pos_hoc

my_comparisons <- list(c("None", "Central"), 
                    c("None", "Peripheral"), 
                    c("Central", "Peripheral"))

plot_discharge <- ggplot(cont_vars %>% 
         filter(grouped_var == "time to first discharge"), 
       aes(x = type, y = value, fill = type)) + 
  geom_boxplot() + 
  theme_bw()

plot_discharge + stat_compare_means(test = "kruskal.wallis", label.y = 100) + 
  stat_compare_means(comparisons = my_comparisons, method = "wilcox")


plot_elix <- ggplot(cont_vars %>% 
         filter(grouped_var == "Elixhauser score"), 
       aes(x = type, y = value, fill = type)) + 
  geom_boxplot() + 
  theme_bw()

plot_elix + stat_compare_means(test = "kruskal.wallis", label.y = 20) + 
  stat_compare_means(comparisons = my_comparisons, method = "wilcox")

elix_score = cont_vars %>% filter(grouped_var == "Elixhauser score")

pos_hoc = dunnTest(elix_score$value ~ elix_score$type,
              data=elix_score,
              method="bh")

pos_hoc <- pos_hoc$res
pos_hoc
```

### Diagnoses

```{r}
neuro_icds_10 <-
  readxl::read_excel("public-data/2020-02-22_neuro-icd10_CNSvPNS.xlsx") %>%
  rename(
    "icd" = `ICD-10`,
    "pns_cns" = `Nervous system Involvement (1=central, 2=peripheral)`
  ) %>%
  mutate(pns_cns = as.factor(pns_cns) %>% fct_recode(
    Central = "1",
    Peripheral = "2"
  )) %>%
  select(icd, `Neurological Disease Category`, pns_cns, `ICD-10 Description`) %>%
  rename("description" = `ICD-10 Description`) %>%
  mutate(concept_type = "icd-10")

neuro_icds_9 <- read.csv("public-data/icd9_tab_CNSvPNS.csv") %>%
  rename(
    "Neurological Disease Category" = "Neurological.Disease.Category",
    "pns_cns" = `Nervous.system.Involvement..1.central..2.peripheral.`,
    "icd_description" = `icd9_desc`
  ) %>%
  mutate(
    pns_cns = as.factor(pns_cns) %>% fct_recode(
      Central = "1",
      Peripheral = "2"
    ),
    concept_type = "DIAG-ICD9"
  ) %>%
  select(icd, `Neurological Disease Category`, pns_cns, icd_description) %>%
  rename("description" = icd_description) %>%
  mutate(concept_type = "icd-9")

icds <- rbind(neuro_icds_10, neuro_icds_9)

diag_table_list <- list()

for (i in sorted_sites) {
  tmp <- get(i)
  tmp_diag <- tmp[[c(
    "first_hosp_results",
    "icd_tables",
    "demo_table"
  )]]
  tmp_diag$site <- tmp[["site"]]
  diag_table_list[[i]] <- tmp_diag %>%
    filter(variable == "sex.female" | variable == "sex.male") %>%
    select(site, contains("n_var"))
}

diag_table_wide <- bind_rows(diag_table_list)


diag_counts <- colSums(Filter(is.numeric, diag_table_wide), na.rm = TRUE) %>% 
  data.frame() %>% 
  mutate(perc = round(./N * 100, 1))

diag_counts <- tibble::rownames_to_column(diag_counts, "icd") %>%
  mutate(icd = gsub("n_var_", "", icd)) %>%
  rename(`Number of Patients` = ".") %>%
  full_join(., icds, by = "icd") %>%
  dplyr::arrange(desc(`Number of Patients`)) %>% 
  mutate(`Number of Patients (% of Cohort)` = paste(`Number of Patients`, "(", perc, ")", sep = " ")) %>% 
  select(pns_cns, `Neurological Disease Category`, concept_type, 
         icd, description, `Number of Patients (% of Cohort)`) %>% 
    rename(Code = "icd",
         `Nervous System` = "pns_cns",
         Description = "description",
         `ICD Version` = "concept_type") %>% 
  mutate(`Number of Patients (% of Cohort)` = if_else(`Number of Patients (% of Cohort)` == "NA ( NA )", "0 ( 0 )", `Number of Patients (% of Cohort)`))

datatable(diag_counts)

write.csv(diag_counts, "Manuscript/Supp.Table2_diagnoses.csv", row.names = FALSE)
```

### Comordities

Stratified by CPNS Diseases

*Note: Diabetes is duplicated. We will choose 1 of the diabetes codes.*

**List from ICD package icd/data/mappingNames

```{r}
# HTN marked together as combined, but DM not.
names_elix_htn <- list(
  "01" = "Congestive heart failure",
  "02" = "Cardiac arrhythmias",
  "03" = "Valvular disease",
  "04" = "Pulmonary circulation disorders",
  "05" = "Peripheral vascular disorders",
  "06a" = "Hypertension, uncomplicated",
  "06b" = "Hypertension, complicated",
  "07" = "Paralysis",
  "08" = "Other neurological disorders",
  "09" = "Chronic pulmonary disease",
  "10" = "Diabetes, uncomplicated",
  "11" = "Diabetes, complicated",
  "12" = "Hypothyroidism",
  "13" = "Renal failure",
  "14" = "Liver disease",
  "15" = "Peptic ulcer disease excluding bleeding",
  "16" = "HIV/AIDS",
  "17" = "Lymphoma",
  "18" = "Metastatic cancer",
  "19" = "Solid tumor without metastasis",
  "20" = "Rheumatoid arthritis/collagen vascular diseases",
  "21" = "Coagulopathy",
  "22" = "Obesity",
  "23" = "Weight loss",
  "24" = "Fluid and electrolye disorders",
  "25" = "Blood loss anemia",
  "26" = "Deficiency anemias",
  "27" = "Alcohol abuse",
  "28" = "Drug abuse",
  "29" = "Psychoses",
  "30" = "Depression"
)

# Elixhauser with HTN combined:
comorb_list <- names_elix_htn
comorb_list["06b"] <- NULL
comorb_list["06a"] <- "Hypertension, combined"
names(comorb_list)[6] <- "06"

Comorbidity <- unlist(comorb_list)
Comorbidity <- as.data.frame(Comorbidity)

Comorbidity <- tibble::rownames_to_column(Comorbidity, "Abbreviation")

```

```{r}
comorb_table_list <- list()

# modify BCH
BCH_results[["first_hosp_results"]][["cpns_results"]][["elix_obfus_table1"]][["Comorbidity"]]  

df <- BCH_results[["first_hosp_results"]][["cpns_results"]][["elix_obfus_table1"]] %>% 
  arrange(Abbreviation) %>% 
  select(-Comorbidity) %>% 
  left_join(., Comorbidity, by = "Abbreviation")

BCH_results[["first_hosp_results"]][["cpns_results"]][["elix_obfus_table1"]] <- df


for (i in sorted_sites) {
  tmp <- get(i)
  tmp_comorb <- tmp[[c(
    "first_hosp_results",
    "cpns_results",
    "elix_obfus_table1"
  )]]
  tmp_comorb$site <- tmp[["site"]]
  comorb_table_list[[i]] <- tmp_comorb %>%
    filter(!Comorbidity == "Diabetes, uncomplicated") %>% 
    mutate(Comorbidity = if_else(Comorbidity == "Diabetes, complicated", "Diabetes", Comorbidity)) %>% 
    select(site, Comorbidity,  n_Total, n_None, n_Central, n_Peripheral)
}

comorb_table_wide <- bind_rows(comorb_table_list) %>% 
  data.frame() %>% 
  group_by(Comorbidity) %>% 
  mutate(Comorb_Total = sum(n_Total, na.rm = TRUE),
         Comorb_Perc = round(Comorb_Total/as.numeric(tableOne_compiled[1,"N"])*100, 1)) %>% 
  arrange(desc(Comorb_Perc)) %>% 
  mutate(None_Total = sum(n_None, na.rm = TRUE),
         None_Perc = round(None_Total/as.numeric(gsub( " .*$", "", tableOne_compiled[1,"None"])) * 100, 1),
         CNS_Total = sum(n_Central, na.rm = TRUE),
         CNS_Perc = round(CNS_Total/as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Central"])) * 100, 1),
         PNS_Total = sum(n_Peripheral, na.rm = TRUE),
         PNS_Perc = round(PNS_Total/as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Peripheral"])) * 100, 1),
         Comorb_Total = paste(Comorb_Total, "(", Comorb_Perc, ")"),
         None_Total = paste(None_Total, "(", None_Perc, ")"),
         CNS_Total = paste(CNS_Total, "(", CNS_Perc, ")"),
         PNS_Total = paste(PNS_Total, "(", PNS_Perc, ")")) %>% 
  distinct(Comorbidity, Comorb_Total, None_Total, CNS_Total, PNS_Total, None_Perc, CNS_Perc, PNS_Perc) %>% 
  ungroup()

datatable(comorb_table_wide)

write.csv(comorb_table_wide, "demo_results/comorbidity_table_cnps.csv", row.names = FALSE)
```

### CNS vs PNS vs None Analysis

```{r}
# sum of all neuro patients
cns_n = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Central"]))
pns_n = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"Peripheral"]))

neuro_n = sum(cns_n, pns_n)

patients_none = as.numeric(gsub( " .*$", "", tableOne_compiled[1,"None"]))

comorb_table_list <- list()

for (i in sorted_sites) {
  tmp <- get(i)
  tmp_comorb <- tmp[[c(
    "first_hosp_results",
    "cpns_results",
    "elix_obfus_table1"
  )]]
  tmp_comorb$site <- tmp[["site"]]
  comorb_table_list[[i]] <- tmp_comorb %>%
    filter(!Comorbidity == "Diabetes, uncomplicated") %>% 
    mutate(Comorbidity = if_else(Comorbidity == "Diabetes, complicated", "Diabetes", Comorbidity)) %>% 
    select(site, Comorbidity,  n_Total, n_None, n_Peripheral, n_Central)
}


comorb_by_site <- bind_rows(comorb_table_list) %>% 
  data.frame() %>% 
  group_by(Comorbidity) %>% 
  mutate(Comorb_Total = sum(n_Total, na.rm = TRUE),
         Comorb_Perc = round(Comorb_Total/as.numeric(tableOne_compiled[1,"N"])*100, 1),
         None_Total = sum(n_None, na.rm = TRUE),
         None_Perc = round(None_Total/patients_none*100, 1),
         CNS_Total = sum(n_Central, na.rm = TRUE),
         CNS_Perc = round(CNS_Total/cns_n*100, 1),
         PNS_Total = sum(n_Peripheral, na.rm = TRUE),
         PNS_Perc = round(PNS_Total/pns_n*100, 1))
  
write.csv(comorb_by_site, "demo_results/comorbidities_by_site.csv", row.names = FALSE)


comorb_table_wide_stratified <- bind_rows(comorb_table_list) %>% 
  data.frame() %>% 
  group_by(Comorbidity) %>% 
  mutate(Comorb_Total = sum(n_Total, na.rm = TRUE),
         Comorb_Perc = round(Comorb_Total/as.numeric(tableOne_compiled[1,"N"])*100, 1),
         None_Total = sum(n_None, na.rm = TRUE),
         None_Perc = round(None_Total/patients_none*100, 1),
         CNS_Total = sum(n_Central, na.rm = TRUE),
         CNS_Perc = round(CNS_Total/cns_n*100, 1),
         PNS_Total = sum(n_Peripheral, na.rm = TRUE),
         PNS_Perc = round(PNS_Total/pns_n*100, 1)) %>% 
  distinct(Comorbidity, Comorb_Total, Comorb_Perc, None_Total, None_Perc, CNS_Total, CNS_Perc, PNS_Total, PNS_Perc) %>% 
  select(Comorbidity, Comorb_Total, Comorb_Perc, None_Total, None_Perc, CNS_Total, CNS_Perc, PNS_Total, PNS_Perc) %>% 
  arrange(desc(Comorb_Perc)) %>% 
  ungroup()

write.csv(comorb_table_wide_stratified, "demo_results/comorbidities_grouped.csv", row.names = FALSE)

datatable(comorb_table_wide_stratified)
```

**Chi-square analysis - None vs CNS vs PNS**

```{r}
list_of_comorbs <- comorb_table_wide_stratified$Comorbidity

chi_result_list <- list()

for (i in list_of_comorbs) {
  
  comorb <- comorb_table_wide_stratified %>% filter(Comorbidity == paste(i))
  
  build_mat <- comorb %>% 
    select(None_Total, CNS_Total, PNS_Total) %>% 
    mutate(NoCNS_Comorb = cns_n - CNS_Total, 
           NoPNS_Comorb = pns_n - PNS_Total,
           NoNone_Comorb = patients_none - None_Total) %>% 
    select(None_Total, NoNone_Comorb, CNS_Total, NoCNS_Comorb, PNS_Total, NoPNS_Comorb) %>% 
    as.character()
  
  mat <- matrix(as.numeric(build_mat), nrow = 2, ncol = 3)
  chi_result <- chisq.test(mat, correct=FALSE) # Yate's correction may make more of a different with smaller sample size - no large differences appearant when I compared results
  
  pval <- chi_result$p.value 
  x2 <- chi_result$statistic
  chi_results <- data.frame("Comorbidity" = paste(i), "X-squared" = x2, "P-value" = pval)
  
  chi_result_list[[i]] <- chi_results
  
}

chi_result_table <- bind_rows(chi_result_list)
```

Significance when correcting for Bonferroni

p-value = 0.05/(29 comorbs (we collapsed two diabetes into one) 

```{r}
pval_adj = 0.05/29
pval_adj

chi_result_table <- chi_result_table %>% 
  mutate(sig_adj_pval = ifelse(P.value < pval_adj, 1, 0)) %>% 
  arrange(desc(X.squared)) %>%  
  left_join(., comorb_table_wide_stratified %>% 
                                select(Comorbidity, None_Total, None_Perc, CNS_Total, CNS_Perc, PNS_Total, PNS_Perc), by = "Comorbidity") %>% 
  mutate(None_Perc = paste(None_Total, "(", None_Perc, ")"),
         CNS_Perc = paste(CNS_Total, "(", CNS_Perc, ")"),
         PNS_Perc = paste(PNS_Total, "(", PNS_Perc, ")")) %>% 
  select(Comorbidity, None_Perc, CNS_Perc, PNS_Perc, X.squared, P.value, sig_adj_pval) %>% 
  rename(No_Neuro_Perc = "None_Perc") %>% 
  mutate(P.value = if_else(P.value < 0.001, "< 0.001", paste(round(P.value, 3))),
         X.squared = round(X.squared, 1))

write.csv(chi_result_table, "demo_results/chi_square_comorb_stratified_results.csv", row.names = FALSE)
```

### Calculate relative risk for each comorbidity

For each comorbidity, calculate the risk of each neuro group for having the comorbidity. 

e.g, Risk of having hypertension in CNS group = `number of CNS patients with hypertension` / `total number of CNS patients`

We calculate Relative risk by dividing CNS risk / NNC risk

```{r}
rr_calcs <- list()

for (i in list_of_comorbs) {
  
  # https://www.cdc.gov/csels/dsepd/ss1978/lesson3/section5.html
      rr <- comorb_table_wide_stratified %>% 
    filter(Comorbidity == paste(i)) %>% 
    mutate(r_CNS = CNS_Total/Comorb_Total,
           r_PNS = PNS_Total/Comorb_Total,
           r_noComorb_CNS = (cns_n - CNS_Total) / (N - Comorb_Total),
           r_noComorb_PNS = (pns_n - PNS_Total) / (N - Comorb_Total),
           rr_CNS = r_CNS/r_noComorb_CNS,
           rr_PNS = r_PNS/r_noComorb_PNS) 
  
  rr_calcs[[i]] <- rr
  
}

rr_results <- bind_rows(rr_calcs)

## to calculate confidence intervals
#https://sphweb.bumc.bu.edu/otlt/mph-modules/bs/bs704_confidence_intervals/bs704_confidence_intervals8.html

# exposed group - with outcome, without outcome
# non exposed group, with outcome, without outcome
# where variables ending with `_Total` are the total number of CNS, PNS, or NNC patients with the respective comorbidity. variables ending with `_n` are the total numbers in the entire population 

rr_ci_results_list <- list()

for (i in list_of_comorbs) {
  
  mat <- rr_results %>% 
    filter(Comorbidity == paste(i)) %>% 
    mutate(no_cns_comorb = cns_n - CNS_Total, 
           no_none_comorb = patients_none - None_Total, 
           no_pns_comorb = pns_n - PNS_Total) %>% 
    select(CNS_Total, no_cns_comorb, None_Total, no_none_comorb, rr_CNS, 
           PNS_Total, no_pns_comorb, rr_PNS)
      
  # to calculate CIs
  #(n1 - x1)/x1  /n1
  # without outcome / outcome / total
  
  ## CNS RR
  n1 = mat$no_cns_comorb / mat$CNS_Total / cns_n
  n2 = mat$no_none_comorb / mat$None_Total / patients_none
  
  to_square <- sqrt(n1+n2)
  
  l_ci <- log(mat$rr_CNS) - (1.96*to_square)
  u_ci <- log(mat$rr_CNS) + (1.96*to_square)
  
  # need to then take the antilog
  l_ci = exp(l_ci)
  u_ci = exp(u_ci)
  
  cns_rr_results_ci <- data.frame(i, "CNS", mat$rr_CNS, l_ci, u_ci) 
  colnames(cns_rr_results_ci) <- c("Comorbidity", "Neuro", "RR", "l_CI", "u_CI")
  
  ## PNS RR
  ## CNS RR
  n1 = mat$no_pns_comorb / mat$PNS_Total / pns_n
  n2 = mat$no_none_comorb / mat$None_Total / patients_none
  
  to_square <- sqrt(n1+n2)
  
  l_ci <- log(mat$rr_PNS) - (1.96*to_square)
  u_ci <- log(mat$rr_PNS) + (1.96*to_square)
  
  # need to then take the antilog
  l_ci = exp(l_ci)
  u_ci = exp(u_ci)
  
  pns_rr_results_ci <- data.frame(i, "PNS", mat$rr_PNS, l_ci, u_ci) 
  colnames(pns_rr_results_ci) <- c("Comorbidity","Neuro", "RR", "l_CI", "u_CI")
  
  rr_results_ci <- rbind(cns_rr_results_ci, pns_rr_results_ci)
  
  rr_ci_results_list[[i]] <- rr_results_ci
}

rr_ci_results <- bind_rows(rr_ci_results_list) 

rr_tidy_table_cns <- rr_ci_results %>% 
  filter(Neuro == "CNS") %>% 
  mutate(RR = round(RR, 2),
         l_CI = round(l_CI, 2),
         u_CI = round(u_CI, 2)) %>% 
  arrange(-RR)

rr_tidy_table_pns <- rr_ci_results %>% 
  filter(Neuro == "PNS") %>% 
  mutate(RR = round(RR, 2),
         l_CI = round(l_CI, 2),
         u_CI = round(u_CI, 2)) %>% 
  arrange(-RR)

write.csv(rr_tidy_table_cns, "Manuscript/Supp.Table4_RR_cns.csv", row.names = FALSE)
write.csv(rr_tidy_table_pns, "Manuscript/Supp.Table4_RR_pns.csv", row.names = FALSE)
```

```{r}
cns_top_results <- rr_ci_results %>% 
  filter(Neuro == "CNS") %>% 
  arrange(RR) %>% 
  select(Comorbidity) 

rr_ci_results$Comorbidity <-  ordered(rr_ci_results$Comorbidity, levels = cns_top_results$Comorbidity)

ggplot(rr_ci_results %>% 
         group_by(Comorbidity),
       aes(x = RR, y = Comorbidity, color = Neuro)) +
  geom_vline(aes(xintercept = 1), size = .25, linetype = "dashed") + 
    geom_errorbarh(aes(xmax = u_CI, xmin = l_CI), size = 0.5, height = 0.2, color = "gray50") +
    geom_point(size = 2) + 
    scale_x_continuous(breaks = seq(0, 4, 1), labels = seq(0, 4, 1),
                       limits = c(0,4)) + 
  ylab("") + 
  xlab("Relative Risk")

svg("manuscript/figures/relative_risk_CNS.svg")
cns_rr_plot <- ggplot(rr_ci_results %>% 
         filter(Neuro == "CNS"),
       aes(x = RR, y = Comorbidity)) +
  geom_vline(aes(xintercept = 1), size = .25, linetype = "dashed") + 
    geom_errorbarh(aes(xmax = u_CI, xmin = l_CI), size = 0.5, height = 0.2, color = "gray50") +
    geom_point(size = 1.5, color = "tomato") + 
    scale_x_continuous(breaks = seq(0, 4, 1), labels = seq(0, 4, 1),
                       limits = c(0,4)) + 
  ylab("") + 
  xlab("Relative Risk") + 
  ggtitle("A. CNS Patients") + 
  theme(axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        title = element_text(size = 16, face = "bold"))
print(cns_rr_plot)
dev.off()

pns_top_results <- rr_ci_results %>% 
  filter(Neuro == "PNS") %>% 
  arrange(RR) %>% 
  select(Comorbidity) 

rr_ci_results$Comorbidity <-  ordered(rr_ci_results$Comorbidity, levels = pns_top_results$Comorbidity)

svg("manuscript/figures/relative_risk_PNS.svg")
pns_rr_plot <- ggplot(rr_ci_results %>% 
         filter(Neuro == "PNS"),
       aes(x = RR, y = Comorbidity)) +
  geom_vline(aes(xintercept = 1), size = .25, linetype = "dashed") + 
    geom_errorbarh(aes(xmax = u_CI, xmin = l_CI), size = 0.5, height = 0.2, color = "gray50") +
    geom_point(size = 1.5, color = "slateblue") + 
    scale_x_continuous(breaks = seq(0, 1.5, 0.5), labels = seq(0, 1.5, 0.5),
                       limits = c(0,1.5)) + 
  ylab("") + 
  xlab("Relative Risk") + 
  ggtitle("B. PNS Patients") + 
  theme(axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        title = element_text(size = 16, face = "bold"))
print(pns_rr_plot)
dev.off()


ggsave("manuscript/figures/relative_risk.svg", grid.arrange(cns_rr_plot, pns_rr_plot, ncol=2), width = 20, height = 8)
```



### LPCA deviance explained

How much deviance is explained with 10 principal components for 30 comorbidity types?

Across sites, 10 principal components explained above 75% of the deviance.

```{r}
pca_dev <- list()
for (i in sorted_sites) {
  tmp <- get(i)
  if (!is.null(tmp$deviance_expl)) {
    pca_dev[[i]] <- data.frame(site = tmp$site, dev_expl = tmp$deviance_expl)
  }
}


pca_plot <- bind_rows(pca_dev) %>%
  ggplot(aes(x = fct_reorder(site, -dev_expl), y = dev_expl, group = 1)) +
  geom_point() +
  geom_line() +
  coord_cartesian(ylim = c(0, 1)) +
  labs(y = "Proportion of Deviance explained", x = NULL) + 
  theme(axis.text.x=element_text(angle=90, hjust=1)); pca_plot

ggsave("manuscript/figures/pca_deviance.png", pca_plot, height = 4, width = 6)
```


