---
title: "meta-survival-curves"
author: "Meg Hutch"
date: "12/8/2021"
output: html_document
---

Generate survival curves

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(metafor)
library(meta)
source("R/forester_custom.R")
```

```{r}
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}
rm(rdas, rda)

# create a list of all rda files with "result" suffix
# check for sites we may want to exclude
googlesheets4::gs4_deauth()
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

sorted_sites <- site_avails %>%
  filter(date_v3_received == 1) %>%
  pull(siteid) %>%
  paste("results", sep = "_")
```


```{r}
site_results <- mget(ls(pattern = "results"))
site_results <- site_results[sorted_sites]
```


change ```neuro_type_analyze``` in order to change analysis to 'cpns_results' or 'binary_results'

```{r}
neuro_type_analyze <- "cpns_results"
```

## Define outcomes

```{r}
outcomes <-
  c(
    "time_first_discharge_reg_elix",
    "time_severe_reg_elix",
    "time_deceased_reg_elix"
  )
```


## Define functions to perform meta-analysis to generate curves

```{r}
get_life_row <- function(df,
                         outcome = "time_severe_reg_elix",
                         period = "first_hosp_results",
                         neuro_type = neuro_type_analyze) {
  life_output <- df[[c(period, neuro_type, outcome, "average_survival", "survf")]]
  bind_cols(life_output[c("surv", "std.err", "time", "strata")]) %>%
    mutate(
      site = df$site,
      #n_site = df[[c(period, neuro_type, outcome, "cox")]]
    )
}
#df = site_results[[1]]
get_cox_row <- function(df,
                        outcome = "time_severe_reg_elix",
                        period = "first_hosp_results",
                        neuro_type = neuro_type_analyze) {
  cox_output <- df[[c(period, neuro_type, outcome, "cox")]]
  coefficients(cox_output) %>%
    data.frame() %>%
    mutate(
      site = df$site
      #n_site = cox_output$n
    ) %>%
    rownames_to_column("variable")
}
```

```{r}
meta_results <- list()

for (outcome_i in outcomes) {
  meta_results[[outcome_i]] <-
    site_results %>%
    lapply(get_life_row, outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}

res_dat <- bind_rows(meta_results)
res_dat_surv <- res_dat[[1]] %>% data.frame()
colnames(res_dat_surv) <- c("None", "PNS", "CNS")

res_dat_std.err <- res_dat[[2]] %>% data.frame()
colnames(res_dat_std.err) <- c("None", "PNS", "CNS")
res_dat_std.err <- res_dat_std.err  %>%
  cbind(., res_dat[3:5]) %>% 
  pivot_longer(cols = None:CNS,  names_to = "strata", values_to = "std.err")

res_dat_surv <- res_dat_surv %>%
  cbind(., res_dat[3:5]) %>% 
  pivot_longer(cols = None:CNS,  names_to = "strata", values_to = "surv") %>% 
  left_join(., res_dat_std.err) %>% 
  mutate(std.err = ifelse(is.nan(std.err), NA, std.err)) %>%
  filter(!time < 0) %>% 
  add_count(site, strata, outcome, name = "n_timepoints") %>%
  complete(time, site, nesting(strata, outcome)) %>%
  mutate(surv = if_else(is.na(surv) & time == 0, 1, surv)) %>%
  group_by(site, strata, outcome) %>%
  arrange(time) %>% 
  fill(surv, .direction = "down") %>%
  fill(std.err, n_timepoints, .direction = "down") %>%
  #fill(std.err, n_site, n_timepoints, .direction = "downup") %>%
  #filter(n_timepoints >= 5, time >= 0) %>%
  ungroup()

```

### Evaluate survival curves by site

```{r}
res_dat_surv$strata <- as.factor(res_dat_surv$strata)
res_dat_surv$strata <- fct_recode(res_dat_surv$strata, "NNC" = "None")

res_dat_surv$strata <- factor(res_dat_surv$strata, levels=c("NNC", "CNS", "PNS"), labels=c("NNC", "CNS", "PNS"))

group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")

site_names <- names(site_results) %>% 
  gsub("_results", "", .)

# calculate CIs
zval <- qnorm(1- (1-0.95)/2, 0, 1)
standard_error <- function(x) sd(x, na.rm = TRUE) / sqrt(length(x)) # Create own function


pdf(file="manuscript/figures/site_level_survival_curves.pdf", height = 4, width = 6)  

for(i in site_names) {
  
  plot <- res_dat_surv %>%
    mutate(outcome = factor(outcome, levels = outcomes) %>%
             fct_recode(
               "Mortality" = "time_deceased_reg_elix",
               "Severity" = "time_severe_reg_elix",
               "Time to first discharge" = "time_first_discharge_reg_elix"
             )) %>% 
    filter(site == i) %>% 
    group_by(outcome, strata) %>% 
    mutate(
      lt_hat = log(-log(surv)),
      se_lt_hat = standard_error(surv)) %>% 
    ungroup() %>% 
    mutate(ci_lower = exp(-exp(log(-log(surv)) + zval*se_lt_hat)),
           ci_upper = exp(-exp(log(-log(surv)) - zval*se_lt_hat))) %>% 
    filter(time <= 60) %>% 
    ggplot(aes(
    x = time, y = surv,
    color = strata,
    fill = strata,
  )) +
  geom_line(aes()) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper, fill = strata), alpha = 0.2, linetype = 0, show.legend = FALSE) + 
  labs(color = NULL, y = NULL) +
  scale_colour_manual(values = group.colors) + 
  scale_fill_manual(values = group.colors) + 
  facet_wrap(~outcome, ncol = 3) +
  coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
  xlab("Time (days)") + 
  ylab("Event Probability") +
  theme_classic() + 
  labs(color = "Neuro Status",
       fill = "") + 
  theme(legend.position="top")
  
  print(plot + ggtitle(paste(i)) + 
           theme(plot.title = element_text(hjust = 0.5)))
  
  
}

dev.off()

```

## Remove sites excluded from meta-analysis

```{r}
res_dat_surv <- res_dat_surv %>% 
  filter(!site %in% c("NUH", "BCH", "GOSH"))

nrow(data.frame(unique(res_dat_surv$site)))
```

```{r}
get_life_table <- function(df,
                         outcome = "time_severe_reg_elix",
                         period = "first_hosp_results",
                         neuro_type = neuro_type_analyze) {
  life_output <- df[[c(period, neuro_type, outcome, "event_table_obfs")]] %>%
    mutate(
      site = df$site,
      #n_site = df[[c(period, neuro_type, outcome, "cox")]]
    )
}

life_tables <- list()

for (outcome_i in outcomes) {
  life_tables[[outcome_i]] <-
    site_results %>%
    lapply(get_life_table, outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}


# should calculate the number at risk at each time point
# then calculate the cumulative number of events and censored - can then clarify cumulative counts in the figure legend
km_life_table <- bind_rows(life_tables) %>% 
  filter(!site %in% c("BCH", "GOSH", "NUH")) %>% 
  group_by(status, outcome) %>%
  complete(time = 1:max(time)) %>%  
  #mutate(count = n_distinct(time)) %>% 
  fill(n.risk, .direction = "down") %>%
  group_by(status, outcome, time) %>% 
  mutate(`N risk` = sum(n.risk, na.rm = TRUE),
         cumulative.n.censor = sum(n.censor, na.rm = TRUE),
         cumulative.n.event = sum(n.event, na.rm = TRUE)) %>% 
  group_by(outcome, status) %>% 
  distinct(time, outcome, `N risk`, status, cumulative.n.censor, cumulative.n.event) %>% 
  mutate(`Cumulative N censor` = cumsum(ifelse(is.na(cumulative.n.censor), 0, cumulative.n.censor)) + cumulative.n.censor*0,
         `Cumulative N event` = cumsum(ifelse(is.na(cumulative.n.event), 0, cumulative.n.event)) + cumulative.n.event*0) %>% 
  distinct(time, outcome, status, `N risk`, `Cumulative N censor`, `Cumulative N event`)

total_n_analysis = km_life_table %>% 
  filter(time == 1) %>% 
  distinct(outcome, status, `N risk`, `Cumulative N censor`, `Cumulative N event`) %>% 
  group_by(outcome) %>% 
  mutate(n_analysis = sum(`N risk`,`Cumulative N event`)) 

# %>% 
#   filter(time %in% c(1, 30, 60)) %>% 
#   ungroup() %>% 
#   arrange(outcome)

km_life_table_bch <- bind_rows(life_tables) %>% 
  filter(site == "BCH") %>% 
  group_by(status, outcome) %>%
  complete(time = 1:max(time)) %>%  
  fill(n.risk, .direction = "down") %>%
  group_by(status, outcome, time) %>% 
  mutate(`N risk` = sum(n.risk, na.rm = TRUE),
         cumulative.n.censor = sum(n.censor, na.rm = TRUE),
         cumulative.n.event = sum(n.event, na.rm = TRUE)) %>% 
  group_by(outcome, status) %>% 
  distinct(time, outcome, `N risk`, status, cumulative.n.censor, cumulative.n.event) %>% 
  mutate(`Cumulative N censor` = cumsum(ifelse(is.na(cumulative.n.censor), 0, cumulative.n.censor)) + cumulative.n.censor*0,
         `Cumulative N event` = cumsum(ifelse(is.na(cumulative.n.event), 0, cumulative.n.event)) + cumulative.n.event*0) %>% 
  distinct(time, outcome, status, `N risk`, `Cumulative N censor`, `Cumulative N event`) %>% 
  filter(time %in% c(1, 30, 60)) %>% 
  ungroup() %>% 
  arrange(outcome)

km_life_table_gosh <- bind_rows(life_tables) %>% 
  filter(site == "GOSH") %>% 
  group_by(status, outcome) %>%
  complete(time = 1:max(time)) %>%  
  fill(n.risk, .direction = "down") %>%
  group_by(status, outcome, time) %>% 
  mutate(`N risk` = sum(n.risk, na.rm = TRUE),
         cumulative.n.censor = sum(n.censor, na.rm = TRUE),
         cumulative.n.event = sum(n.event, na.rm = TRUE)) %>% 
  group_by(outcome, status) %>% 
  distinct(time, outcome, `N risk`, status, cumulative.n.censor, cumulative.n.event) %>% 
  mutate(`Cumulative N censor` = cumsum(ifelse(is.na(cumulative.n.censor), 0, cumulative.n.censor)) + cumulative.n.censor*0,
         `Cumulative N event` = cumsum(ifelse(is.na(cumulative.n.event), 0, cumulative.n.event)) + cumulative.n.event*0) %>% 
  distinct(time, outcome, status, `N risk`, `Cumulative N censor`, `Cumulative N event`) %>% 
  filter(time %in% c(1, 30, 60)) %>% 
  ungroup() %>% 
  arrange(outcome)

write.csv(km_life_table, "manuscript/tables/km_life_table_all.csv", row.names = FALSE)
write.csv(km_life_table_bch, "manuscript/tables/km_life_table_all_bch.csv", row.names = FALSE)
write.csv(km_life_table_gosh, "manuscript/tables/km_life_table_all_gosh.csv", row.names = FALSE)
```

### Weight each site 

Here we will weight each site by the inverse of its variance calculated from the CNS and PNS meta-analysis models. We will take the average of the CNS and PNS weights

```{r}
load("survival_model/cns_weights.rda")
load("survival_model/pns_weights.rda")

# rename weight column
cns_weights <- cns_weights %>% 
  rename("cns_weight" = Weight.random) %>% 
  select(-strata)

pns_weights <- pns_weights %>% 
  rename("pns_weight" = Weight.random) %>% 
  select(-strata) 

## average the weights
avg_weights <- cns_weights %>% 
  left_join(., pns_weights, by = c("analysis", "studlab")) %>% 
  mutate(cns_weight = as.numeric(cns_weight),
         pns_weight = as.numeric(pns_weight),
         avg_weight = rowMeans(cbind(cns_weight, pns_weight), na.rm = TRUE)) %>% 
  rename("outcome" = analysis,
         "site" = studlab)
```

### Generate survival curves

```{r}
#chuan's code

## y is the vector of beta coefficients; 
## s is the vector of SE of beta coefficients;
## wt is the weight (e.g, number of events, make sure it does not change over time)

# Meg added the rule to handle cases when v.between is a negative number based on the following reference which explains: 
#https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/heterogeneity.html
# the value of I2 cannot be lower than 0%, so if Q happens to be smaller than K-1,we simply use 0 instead of a negative value.
metaFUN.randomeffect=function(y, s, wt){
  mm=c(y%*%wt/sum(wt))
  df=length(y)-1
  C=sum(wt)-sum((wt)^2)/sum(wt)
  Q=wt%*%(y-mm)^2
  k = length(y)
  if (Q < k-1) {
  v.between=0
} else {
  v.between=c((Q-df)/C); v.between
}
  ww=1/(s^2+v.between)
  ss=sqrt(1/sum(ww))
  data.frame(pool_mean=mm, pool_se=ss)
}

zval <- qnorm(1- (1-0.95)/2, 0, 1)

meta_surv_df <- res_dat_surv %>%
  left_join(., avg_weights, by = c("site", "outcome")) %>%
  ungroup() %>%  
  as.data.frame() %>% 
  filter(!is.na(surv)) %>% 
  group_by(strata, outcome, time) %>%
  mutate(
    surv = metaFUN.randomeffect(surv, std.err, avg_weight)$pool_mean,
    se = metaFUN.randomeffect(surv, std.err, avg_weight)$pool_se
  ) %>%
  mutate(
    strata = str_replace(strata, "neuro_post=", ""),
    outcome = factor(outcome, levels = outcomes) %>%
      fct_recode(
        "Mortality" = "time_deceased_reg_elix",
        "Severity" = "time_severe_reg_elix",
        "Discharge" = "time_first_discharge_reg_elix"
      )
  ) %>% 
    mutate(ci_l = surv - se*zval,
           ci_u = surv + se*zval) %>% 
  distinct(outcome, strata, time, surv, se, ci_l, ci_u)

# refactor
meta_surv_df$strata <- as.factor(meta_surv_df$strata)

meta_surv_df$strata <- factor(meta_surv_df$strata, 
                              levels=c("NNC", "CNS", "PNS"),
                              labels=c("NNC", "CNS", "PNS"))

group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")

surv_curves <- meta_surv_df %>%
  filter(time <= 60) %>% 
  ggplot(aes(
    x = time, y = surv,
    color = strata,
    fill = strata,
  )) +
  geom_line(aes()) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u, fill = strata), alpha = 0.2, linetype = 0, show.legend = FALSE) + 
  labs(color = NULL, y = NULL) +
  scale_colour_manual(values = group.colors) + 
  scale_fill_manual(values = group.colors) + 
  facet_wrap(~outcome, ncol = 3) +
coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
  xlab("Time (days)") + 
  ylab("Event Probability") +
  theme_classic() + 
  labs(color = "Neuro Status",
       fill = "") + 
  theme(legend.position="top"); surv_curves

ggsave("manuscript/figures/survival_curves.png", surv_curves, height = 4, width = 6)
```
