---
title: "Metaanalysis"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(meta)
library(gridGraphics)
library(gridExtra)
library(ggpubr)
library(DT)
library(kableExtra)
library(gridExtra)
library(tidyverse)
library(patchwork)
library(stringr)
#devtools::install_github("rdboyes/forester")
library(forester)
```

```{r}
load('results/NWU_results.rda')
load('results/UPENN_results.rda')
load('results/UPITT_results.rda')
load('results/APHP_results.rda')
load('results/FRBDX_results.rda')
load('results/ICSM_results.rda')
load('results/MGB_results.rda')
load('results/HPG23_results.rda')
```

## Conduct Random-Effects Meta-Analysis

Here we conduct meta-analysis on outcomes occurring within the first hospital stay.

```{r}
get_site <- function(x){
  x$site
}

get_result_row <- function(df,
                           outcome = 'n_stay_reg_elix',
                           period = 'first_hosp_results',
                           neuro_type = 'cpns_results',
                           neuro_chr = 'neuro_postCentral') {
  # neuro_chr <- switch(neuro_type,
  #   cpns_results = 'neuro_postPeripheral',
  #   binary_results = 'neuro_postneuro_cond'
  # )
  df[[c(period, neuro_type, outcome, 'coefficients')]] %>%
    as.data.frame() %>%
    rownames_to_column('term') %>%
    mutate(site = get_site(df)) %>%
    filter(grepl(neuro_chr, term))
}

outcomes <-
  c(
    "n_stay_reg_elix",
    "severe_reg_elix",
    "deceased_reg_elix",
    "n_readmit_reg_elix",
    "readmit_reg_elix",
    "time_severe_reg_elix",
    "time_deceased_reg_elix",
    "time_readmit_reg_elix" 
  )

meta_results <- list()
for (outcome_i in outcomes) {
  meta_results[[outcome_i]] <-
    list(NWU_results, UPENN_results, UPITT_results, 
         APHP_results, ICSM_results, FRBDX_results, 
         MGB_results, HPG23_results) %>% # add other results here
    lapply(get_result_row, outcome = outcome_i) %>%
    bind_rows() %>%
    metagen(
      Estimate,
      `Std. Error`,
      data = .,
      sm = 'MD',
      comb.random = TRUE,
      comb.fixed = FALSE,
      #method.tau = "SJ",
      hakn = FALSE,
      prediction=TRUE,
      studlab = site
      
    )
}
```

_Note_: We will probably want to examine PNS and Both later.

```{r}
ma_combine = list()

for (i in names(meta_results)) {
  TE = meta_results[[i]][["TE"]]
  seTE = meta_results[[i]][["seTE"]]
  studlab = meta_results[[i]][["studlab"]]
  Weight = meta_results[[i]][["w.random"]]
  upper = meta_results[[i]][["upper"]]
  lower = meta_results[[i]][["lower"]]
  TE.random = meta_results[[i]][["TE.random"]]
  lower.random = meta_results[[i]][["lower.random"]]
  upper.random = meta_results[[i]][["upper.random"]]
  pval.random = meta_results[[i]][["pval.random"]]
  I2 = meta_results[[i]][["I2"]]
  analysis = paste(i)
  df <- cbind(studlab, TE, seTE, Weight, upper, lower, TE.random, lower.random, upper.random,
              pval.random, I2,analysis)
  ma_combine[[i]] <- df
}

combined_results <- do.call(rbind.data.frame, ma_combine)
combined_results$TE <- as.numeric(as.character(combined_results$TE))
combined_results$seTE <- as.numeric(as.character(combined_results$seTE))
combined_results$Weight <- as.numeric(as.character(combined_results$Weight))
combined_results$upper <- as.numeric(as.character(combined_results$upper))
combined_results$lower <- as.numeric(as.character(combined_results$lower))
combined_results$TE.random <- as.numeric(as.character(combined_results$TE.random))
combined_results$lower.random <- as.numeric(as.character(combined_results$lower.random))
combined_results$upper.random <- as.numeric(as.character(combined_results$upper.random))
combined_results$pval.random <- as.numeric(as.character(combined_results$pval.random))
combined_results$I2 <- as.numeric(as.character(combined_results$I2))


combined_results <- combined_results %>% mutate(TE = round(TE,2),
                                                seTE = round(seTE,4),
                                                Weight = round(Weight,1),
                                                CI.High = round(upper, 1),
                                                CI.Low = round(lower, 1),
                                                #CI = paste("(", CI.Low, ",", CI.High, ")"),
                                                TE.random = round(TE.random, 1),
                                                lower.random = round(lower.random, 1), 
                                                upper.random = round(upper.random, 1),
                                                CI.random = paste("(", lower.random, ",", upper.random, ")"),
                                                #pval.random = round(pval.random, 4),
                                                I2 = round(I2, 2)*100) %>%
  select(-upper, -lower) %>%
  rename("Site" = studlab, 
         "Estimate" = TE, 
         "p-value" = pval.random,
         "CI" = CI.random)
                                                


# Record analysis name to look nicer
combined_results$analysis <- recode(combined_results$analysis,
                                    'n_stay_reg_elix' = 'Length of Stay',
                                    'severe_reg_elix' = 'Severe COVID-19',
                                    'deceased_reg_elix' = 'Mortality',
                                    'n_readmit_reg_elix' = 'Number of Readmissions',
                                    'readmit_reg_elix' = 'Readmission',
                                    'time_severe_reg_elix' = 'Time to Severity',
                                    'time_deceased_reg_elix' = 'Time to Mortality',
                                    'time_readmit_reg_elix' = 'Time to Readmission')
```

Add blank rows to facilitate formatting

```{r}
df_new <- as.data.frame(lapply(combined_results, as.character), stringsAsFactors = FALSE)
combined_results <- head(do.call(rbind, by(df_new, combined_results$analysis, rbind, "")), -1 )

combined_results <- combined_results %>% 
  add_row(.before = 1)
```

hide NA values using a space
```{r}
combined_results[is.na(combined_results)] <- ""
```

Carry over name of the analysis to the blank row

```{r}
combined_results$Site <- as.character(combined_results$Site)
combined_results$analysis <- as.character(combined_results$analysis)

combined_results <- combined_results %>% 
  mutate(Site = if_else(Site == "", lead(analysis), Site)) %>%
  select(-analysis) %>%
  rename("Analysis" = Site)
```

```{r}
combined_results$Estimate <- as.numeric(as.character(combined_results$Estimate))
combined_results$seTE <- as.numeric(as.character(combined_results$seTE))
combined_results$Weight <- as.numeric(as.character(combined_results$Weight))
combined_results$CI.High <- as.numeric(as.character(combined_results$CI.High))
combined_results$CI.Low <- as.numeric(as.character(combined_results$CI.Low))
combined_results$TE.random <- as.numeric(as.character(combined_results$TE.random))
combined_results$p.value <- as.numeric(as.character(combined_results$p.value))
combined_results$I2 <- as.numeric(as.character(combined_results$I2))
```

Indent site results

```{r}
combined_results$Analysis <- ifelse(is.na(combined_results$Estimate),
                         combined_results$Analysis,
                         paste0("   ", combined_results$Analysis))
```

Manually change row names to make it easier to subset

```{r}
rownames_change <- combined_results %>% filter(is.na(Estimate)) %>% row.names()

rownames(combined_results)[rownames(combined_results) == "...1"] <- "Length of Stay"
rownames(combined_results)[rownames(combined_results) == "Length of Stay.8"] <- "Severe"
rownames(combined_results)[rownames(combined_results) == "Severe COVID-19.91"] <- "Mortality"
rownames(combined_results)[rownames(combined_results) == "Mortality.8"] <- "Number of Readmissions"
rownames(combined_results)[rownames(combined_results) == "Number of Readmissions.9"] <- "Readmission"
rownames(combined_results)[rownames(combined_results) == "Readmission.9"] <- "Time to Severity"
rownames(combined_results)[rownames(combined_results) == "Time to Severity.8"] <- "Time to Mortality"
rownames(combined_results)[rownames(combined_results) == "Time to Mortality.8"] <- "Time to of Readmission"
```

Additional formatting to integrate the mixed-effect meta analysis results with the regression estimates

```{r}
combined_results$Estimate <- as.numeric(as.character(combined_results$Estimate))
combined_results$seTE <- as.numeric(as.character(combined_results$seTE))
combined_results$Weight <- as.numeric(as.character(combined_results$Weight))
combined_results$CI.High <- as.numeric(as.character(combined_results$CI.High))
combined_results$CI.Low <- as.numeric(as.character(combined_results$CI.Low))
combined_results$TE.random <- as.numeric(as.character(combined_results$TE.random))
combined_results$I2 <- as.numeric(as.character(combined_results$I2))
combined_results$p.value <- as.numeric(as.character(combined_results$p.value))

combined_results[combined_results == ""] <- NA

combined_results <- combined_results %>%
  fill(TE.random, upper.random, lower.random, p.value, CI, .direction = "up")

# Make the site level information NA for the following columns
combined_results$TE.random <- ifelse(is.na(combined_results$Estimate), combined_results$TE.random, NA)
combined_results$p.value <- ifelse(is.na(combined_results$Estimate), combined_results$p.value, NA)
combined_results$I2 <- ifelse(is.na(combined_results$Estimate), combined_results$I2, NA)
combined_results$CI <- ifelse(is.na(combined_results$Estimate), combined_results$CI, NA)


# convert back to numeric
combined_results$upper.random <- as.numeric(as.character(combined_results$upper.random))
combined_results$lower.random <- as.numeric(as.character(combined_results$lower.random))

# move meta analysis results to the same columns as the site regression estimates 
combined_results$Estimate <- ifelse(is.na(combined_results$Estimate), combined_results$TE.random, combined_results$Estimate)

combined_results$CI.High <- ifelse(is.na(combined_results$CI.High), combined_results$upper.random, combined_results$CI.High)

combined_results$CI.Low <- ifelse(is.na(combined_results$CI.Low), combined_results$lower.random, combined_results$CI.Low)

# convert back to numeric
combined_results$CI.High <- as.numeric(as.character(combined_results$CI.High))
combined_results$CI.Low <- as.numeric(as.character(combined_results$CI.Low))

# create new 'Estimate' column that we can have CIs - this will allow a nicer 
# format the p-values so we don't lose trailing zeros which occurs with as.character()
combined_results <- combined_results %>% 
  mutate('Estimate ' = paste(Estimate, "(", CI.Low, ",", CI.High, ")"),
         p.value_round = round(p.value, 5),
         sig = if_else(p.value < 0.05, 1, 0))

combined_results$p.value_format <- ifelse(combined_results$p.value_round < 0.00001, "< 0.00001", combined_results$p.value_round)
         
combined_results <- combined_results %>% 
  mutate(p.value_format2 = sprintf("%.5f", combined_results$p.value))

combined_results$p.value_format <- ifelse(combined_results$p.value_format == "< 0.00001", combined_results$p.value_format, combined_results$p.value_format2)

combined_results <- combined_results %>%
  mutate(`P-value` = if_else(sig == 1, paste(p.value_format, "*"), p.value_format))

combined_results$p.value[combined_results$p.value == "NA"] <- ""

combined_results[is.na(combined_results)] <- ""
```


## Readmission, Severity, & Mortality

```{r fig.width=8, message=FALSE, warning=FALSE}
toMatch <- c("Severe", "Mortality", "Readmission")

binary_results <- combined_results %>% 
  slice(grep(paste(toMatch, collapse="|"), row.names(.))) %>% 
  filter(!grepl('Number|Time', row.names(.)))

forester(left_side_data = binary_results[1],
         estimate = binary_results$Estimate,
         ci_low = binary_results$CI.Low,
         ci_high = binary_results$CI.High,
         right_side_data = binary_results[,c(13,18)],
         display = TRUE,
         font_family = "arial",
         arrows = TRUE, 
         arrow_labels = c("Decreased Risk", "Increased Risk"),
         xlim = c(-4,4),
         xbreaks = c(-4, 0, 4),
         file_path = here::here("readmission_severity_mortality.png"))
```

## Time to Events

```{r message=FALSE, warning=FALSE}
toMatch <- c("Time")

time_results <- combined_results %>% 
  slice(grep(paste(toMatch, collapse="|"), row.names(.))) %>% 
  filter(!grepl('Readmission', row.names(.)))

forester(left_side_data = time_results[1],
         estimate = time_results$Estimate,
         ci_low = time_results$CI.Low,
         ci_high = time_results$CI.High,
         right_side_data = time_results[,c(13,18)],
         display = TRUE,
         font_family = "arial",
         arrows = TRUE, 
         arrow_labels = c("Decreased Time", "Increased Time"),
         xlim = c(-16,20),
         xbreaks = c(-16, 0, 20),
         file_path = here::here("time_to_events.png"))
```

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
toMatch <- c("Time")

time_results2 <- combined_results %>% 
  slice(grep(paste(toMatch, collapse="|"), row.names(.))) %>% 
  filter(!grepl('Mortality|Severity', row.names(.)))

forester(left_side_data = time_results2[1],
         estimate = time_results2$Estimate,
         ci_low = time_results2$CI.Low,
         ci_high = time_results2$CI.High,
         right_side_data = time_results2[,c(13,18)],
         display = TRUE,
         font_family = "arial",
         arrows = TRUE, 
         arrow_labels = c("Decreased Time", "Increased Time"),
         xlim = c(-45,45),
         xbreaks = c(-45, 0, 45),
         file_path = here::here("time_to_events2.png"))
```

## Length Stay

```{r message=FALSE, warning=FALSE}
toMatch <- c("Length")

day_results <- combined_results %>% 
  slice(grep(paste(toMatch, collapse="|"), row.names(.)))

forester(left_side_data = day_results[1],
         estimate = day_results$Estimate,
         ci_low = day_results$CI.Low,
         ci_high = day_results$CI.High,
         right_side_data = day_results[,c(13,18)],
         display = TRUE,
         font_family = "arial",
         arrows = TRUE, 
         arrow_labels = c("Decreased Length", "Increased Length"),
         xlim = c(-5,25),
         xbreaks = c(-5, 0, 25),
         file_path =here::here("length_of_stay.png"))
```

## Days to Readmissions

```{r message=FALSE, warning=FALSE}
toMatch <- c("Number of Readmissions")

nday_results <- combined_results %>% 
  slice(grep(paste(toMatch, collapse="|"), row.names(.)))

forester(left_side_data = nday_results[1],
         estimate = nday_results$Estimate,
         ci_low = nday_results$CI.Low,
         ci_high = nday_results$CI.High,
         right_side_data = nday_results[,c(13,18)],
         display = TRUE,
         font_family = "arial",
         arrows = TRUE, 
         arrow_labels = c("Decreased Length", "Increased Length"),
         xlim = c(-1,1.5),
         xbreaks = c(-1, 0, 1.5),
         file_path = here::here("n_readmissions.png"))
```
