---
title: "meta-survival-curves"
author: "Meg Hutch"
date: "12/8/2021"
output: html_document
---

Generate survival curves

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(metafor)
library(meta)
source("R/forester_custom.R")
```

```{r}
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}
rm(rdas, rda)

# create a list of all rda files with "result" suffix
# check for sites we may want to exclude
googlesheets4::gs4_deauth()
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

sorted_sites <- site_avails %>%
  filter(date_v3_received == 1) %>%
  pull(siteid) %>%
  paste("results", sep = "_")
```


```{r}
site_results <- mget(ls(pattern = "results"))
site_results <- site_results[sorted_sites]
```


change ```neuro_type_analyze``` in order to change analysis to 'cpns_results' or 'binary_results'

```{r}
neuro_type_analyze <- "cpns_results"
```

## Define outcomes

```{r}
outcomes <-
  c(
    "time_first_discharge_reg_elix",
    "time_severe_reg_elix",
    "time_deceased_reg_elix"
  )
```


## Define functions to perform meta-analysis to generate curves

```{r}
get_life_row <- function(df,
                         outcome = "time_severe_reg_elix",
                         period = "first_hosp_results",
                         neuro_type = neuro_type_analyze) {
  life_output <- df[[c(period, neuro_type, outcome, "average_survival", "survf")]]
  bind_cols(life_output[c("surv", "std.err", "time", "strata")]) %>%
    mutate(
      site = df$site,
      #n_site = df[[c(period, neuro_type, outcome, "cox")]]
    )
}
#df = site_results[[1]]
get_cox_row <- function(df,
                        outcome = "time_severe_reg_elix",
                        period = "first_hosp_results",
                        neuro_type = neuro_type_analyze) {
  cox_output <- df[[c(period, neuro_type, outcome, "cox")]]
  coefficients(cox_output) %>%
    data.frame() %>%
    mutate(
      site = df$site
      #n_site = cox_output$n
    ) %>%
    rownames_to_column("variable")
}

get_surv <- function(surv, std.err, site, weight) {
  if (length(surv) == 1) {
    return(surv)
  } else {
    junk <- rma(y = surv, sei = std.err, weights = weight, method = "DL") # metafor for each strata
    return(c(junk$beta))
  }
}
get_se <- function(surv, std.err, site, weight) {
  if (length(std.err) == 1) {
    return(std.err)
  } else {
    junk <- metafor::rma(y = surv, sei = std.err, weights = weight, method = "DL") # metafor for each strata
    return(c(junk$se))
  }
}
get_pval <- function(surv, std.err, site, weight) {
  if (length(std.err) == 1) {
    return(std.err)
  } else {
    junk <- metafor::rma(y = surv, sei = std.err, weights = weight, method = "DL") # metafor for each strata
    return(c(junk$pval))
  }
}

get_ci.lb <- function(surv, std.err, site, weight) {
  if (length(std.err) == 1) {
    return(std.err)
  } else {
    junk <- metafor::rma(y = surv, sei = std.err, weights = weight, method = "DL") # metafor for each strata
    return(c(junk$ci.lb))
  }
}
get_ci.ub <- function(surv, std.err, site, weight) {
  if (length(std.err) == 1) {
    return(std.err)
  } else {
    junk <- metafor::rma(y = surv, sei = std.err, weights = weight, method = "DL") # metafor for each strata
    return(c(junk$ci.ub))
  }
}
```

```{r}
meta_results <- list()

for (outcome_i in outcomes) {
  meta_results[[outcome_i]] <-
    site_results %>%
    lapply(get_life_row, outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}

res_dat <- bind_rows(meta_results)
res_dat_surv <- res_dat[[1]] %>% data.frame()
colnames(res_dat_surv) <- c("None", "PNS", "CNS")

res_dat_std.err <- res_dat[[2]] %>% data.frame()
colnames(res_dat_std.err) <- c("None", "PNS", "CNS")
res_dat_std.err <- res_dat_std.err  %>%
  cbind(., res_dat[3:5]) %>% 
  pivot_longer(cols = None:CNS,  names_to = "strata", values_to = "std.err")

res_dat_surv <- res_dat_surv %>%
  cbind(., res_dat[3:5]) %>% 
  pivot_longer(cols = None:CNS,  names_to = "strata", values_to = "surv") %>% 
  left_join(., res_dat_std.err) %>% 
  mutate(std.err = ifelse(is.nan(std.err), NA, std.err)) %>%
  filter(!time < 0) %>% 
  add_count(site, strata, outcome, name = "n_timepoints") %>%
  complete(time, site, nesting(strata, outcome)) %>%
  mutate(surv = if_else(is.na(surv) & time == 0, 1, surv)) %>%
  group_by(site, strata, outcome) %>%
  arrange(time) %>% 
  fill(surv, .direction = "down") %>%
  fill(std.err, n_timepoints, .direction = "down") %>%
  #fill(std.err, n_site, n_timepoints, .direction = "downup") %>%
  #filter(n_timepoints >= 5, time >= 0) %>%
  ungroup()

```

### Evaluate survival curves by site

```{r}
res_dat_surv$strata <- as.factor(res_dat_surv$strata)
res_dat_surv$strata <- fct_recode(res_dat_surv$strata, "NNC" = "None")

res_dat_surv$strata <- factor(res_dat_surv$strata, levels=c("NNC", "CNS", "PNS"), labels=c("NNC", "CNS", "PNS"))

group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")

site_names <- names(site_results) %>% 
  gsub("_results", "", .)

pdf(file="manuscript/figures/site_level_survival_curves.pdf", height = 4, width = 6)  

for(i in site_names) {
  
  plot <- res_dat_surv %>%
    mutate(outcome = factor(outcome, levels = outcomes) %>%
             fct_recode(
               "Mortality" = "time_deceased_reg_elix",
               "Severity" = "time_severe_reg_elix",
               "Time to first discharge" = "time_first_discharge_reg_elix"
             )) %>% 
    filter(site == i) %>% 
    filter(time <= 60) %>% 
    ggplot(aes(
      x = time, y = surv,
      color = strata,
    )) +
    geom_line(aes()) +
    labs(color = NULL, y = NULL) +
    facet_wrap(~outcome, ncol = 3) +
    scale_colour_manual(values = group.colors) + 
    coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
    xlab("Time (days)") + 
    ylab("Event Probability") + 
    theme_classic() + 
    theme(legend.text=element_text(size=11)) + 
    guides(colour = guide_legend(override.aes = list(size=2)))
  
  print(plot + ggtitle(paste(i)))
  
  
}

dev.off()

```

## Remove sites excluded from meta-analysis

```{r}
# site_results[['NUH_results']] <- NULL
# site_results[['BCH_results']] <- NULL
# site_results[['GOSH_results']] <- NULL

res_dat_surv <- res_dat_surv %>% 
  filter(!site %in% c("NUH", "BCH", "GOSH"))

nrow(data.frame(unique(res_dat_surv$site)))
```



### Weight each site 

Here we will weight each site by the inverse of its variance calculated from the CNS and PNS meta-analysis models. We will take the average of the CNS and PNS weights

```{r}
load("survival_model/cns_weights.rda")
load("survival_model/pns_weights.rda")

# rename weight column
cns_weights <- cns_weights %>% 
  rename("cns_weight" = Weight.random) %>% 
  select(-strata)

pns_weights <- pns_weights %>% 
  rename("pns_weight" = Weight.random) %>% 
  select(-strata) 

## average the weights
avg_weights <- cns_weights %>% 
  left_join(., pns_weights, by = c("analysis", "studlab")) %>% 
  mutate(cns_weight = as.numeric(cns_weight),
         pns_weight = as.numeric(pns_weight),
         avg_weight = rowMeans(cbind(cns_weight, pns_weight), na.rm = TRUE)) %>% 
  rename("outcome" = analysis,
         "site" = studlab)
```

### Generate survival curves

```{r}
standard_error <- function(x) sd(x, na.rm=TRUE) / sqrt(length(x)) 

meta_surv_df <- res_dat_surv %>%
  left_join(., avg_weights, by = c("site", "outcome")) %>%
  ungroup() %>%  
  as.data.frame() %>% 
  #filter(!site %in% c("GOSH", "BCH")) %>% 
  group_by(strata, outcome, time) %>%
  summarise(
    se = get_se(surv, std.err, site, weight = avg_weight),
    meta_surv = get_surv(surv, std.err, weight = avg_weight)
    #pval = get_pval(surv, std.err, site, weight = avg_weight),
    #ci.lb = get_ci.lb(surv, std.err, site, weight = avg_weight),
    #ci.ub = get_ci.ub(surv, std.err, site, weight = avg_weight),
    #.groups = "drop"
  ) %>%
  #group_by(strata, outcome, time) %>%
  mutate(
    strata = str_replace(strata, "neuro_post=", ""),
    outcome = factor(outcome, levels = outcomes) %>%
      fct_recode(
        "Mortality" = "time_deceased_reg_elix",
        "Severity" = "time_severe_reg_elix",
        "Discharge" = "time_first_discharge_reg_elix"
      )
  )

# refactor
meta_surv_df$strata <- as.factor(meta_surv_df$strata)
meta_surv_df$strata <- fct_recode(meta_surv_df$strata, "NNC" = "None")

meta_surv_df$strata <- factor(meta_surv_df$strata, levels=c("NNC", "CNS", "PNS"), labels=c("NNC", "CNS", "PNS"))

group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")

## test log-log approach
#https://github.com/cran/survival/blob/master/R/survfit.R
# annotated:https://github.com/therneau/survival/blob/5c2cdffbbd3840b2a100e2f9f115de8a5d496c3a/noweb/survfit.Rnw
# specify params for *zvalcalculating confidence intervals
zval <- qnorm(1- (1-0.95)/2, 0,1)
logse = TRUE
# logse param as confirmed via:
#APHP_results[["first_hosp_results"]][["cpns_results"]][["time_severe_reg_elix"]][["average_survival"]][["survf"]]$logse


test = meta_surv_df %>% 
  group_by(outcome, strata) %>% 
  mutate(
    lt_hat = log(-log(meta_surv)),
    se_lt_hat = standard_error(lt_hat)) %>% 
  ungroup() %>% 
  mutate(#se2 = zval * se/log(meta_surv),
         ci_l = exp(-exp(log(-log(meta_surv)) + zval*se_lt_hat)),
         ci_u = exp(-exp(log(-log(meta_surv)) - zval*se_lt_hat)))


surv_curves <- meta_surv_df %>%
  filter(time <= 60) %>% 
  ggplot(aes(
    x = time, y = meta_surv,
    color = strata,
    fill = strata,
  )) +
  geom_line(aes()) +
  #geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.1, linetype = 2) +
  #geom_ribbon(aes(ymin = ci_l, ymax = ci_u, fill = strata), alpha = 0.2, linetype = 0, show.legend = FALSE) + 
  #geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, linetype = 0) + 
  labs(color = NULL, y = NULL) +
  scale_colour_manual(values = group.colors) + 
  scale_fill_manual(values = group.colors) + 
  facet_wrap(~outcome, ncol = 3) +
  # ggrepel::geom_text_repel(
  #   data = . %>% filter(
  #     time == last(time),
  #     outcome == "Mortality"
  #   ),
  #   aes(
  #     label = strata,
  #     x = time + 10,
  #     y = meta_surv,
  #     color = strata
  #   ), direction = "y"
# ) +
coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
  xlab("Time (days)") + 
  ylab("Event Probability") + 
  #guides(color = FALSE) +
  theme_classic() + 
  labs(color = "strata",
       fill = ""); surv_curves

ggsave("manuscript/figures/survival_curves.png", surv_curves, height = 4, width = 6)
```
